Unified Understanding of the Dielectric Nature of Two-Dimensional Materials

### 2018-10-16 paper.tex
Shorten section of theory

In this letter, We study several types of 2D materials of different
electronic and optical properties, including transition metal
dichalcogenides (TMDCs, with the formula MX\(_{\text{2}}\), where M is
a metal in group 4, 6, 10 and X=O, S, Se, Te), metal monochalcogenides
(Ga$_{2}$S$_{2}$, Ga$_{2}$Se$_{2}$), cadmium halides (CdX$_2$, X=Cl,
I), hexagonal boron nitride (BN), graphene derivatives (fluorographene
(C$_{2}$F$_{2}$), graphane (C$_{2}$H$_{2}$)) and phosphorene (P$4$).
For the TMDCs, we consider 2 lattice phases, namely the 2H
(P\(\bar{6}\)m2 space group) and 1T (P3m1 space group).  The elements
involved in this study and the structures of the 2D materials are
shown in Figure \ref{fig-2}a and \ref{fig-2}b, respectively. The
static 2D polarizabilities are calculated from the static dielectric
response of the selected 2D materials using density functional theory
(DFT) with Heyd-Scuseria-Ernzerhof hybrid functionals (HSE06) in the
Vienna Ab Initio Simulation Package (VASP) including spin-orbit
coupling to avoid limitations on the description of band gaps and
dielectric functions. Further details for the first principle
calculations please refer to \textit{Methods}.

Figure \ref{fig-3}a shows the calculated $E_{\mathrm{g}}$ (blue dots)
and polarizabilities (bar plots) of all the 2D materials investigated,
covering a wide bandgap range of over 6 eV. The 2D polarizability
$\alpha $has the unit of Farad, and is more intuitive to be expressed
in the form $\alpha/(4 \pi \varepsilon_{0})$, which has the unit of
[Length] (similar to the molecular polarizability, which has the unit
of $4\pi \varepsilon_{0}\times$[Volume] \cite{Israelachvili_2011}). We
find that $\alpha^{\parallel}$ has a general descending trend when
$E_{\mathrm{g}}$ increases. On the other hand, no apparent trend
between $\alpha^{\perp}$ and $E_{\mathrm{g}}$ is observed (more
details see Supplementary Figure SXX \todo{TBD}). Recently, it is
found that the exciton binding energy $E_{\mathrm{b}}$ of 2D materials
exhibits universal linear relation with $E_{\mathrm{g}}$
\cite{Choi_linear_2015,Olsen_2016_hydrogen,Jiang_2017_Eg_Eb}. Combine
with the fact that the $E_{\mathrm{b}}$ is roughly inversely
proportional to $\alpha^{\parallel}$ \cite{Pulci_2014}, it is
reasonable to guess that a general linear correlation between
$E_{\mathrm{g}}$ and $1/\alpha^{\parallel}$ may exist for 2D
materials. Figure \ref{fig-3}c shows
$(4 \pi \varepsilon_{0})/\alpha^{\parallel}$ (in \AA{}) as a function
of $E_{\mathrm{g}}$ (in eV) for the 2D materials investigated, with a
linear regression slope of ~0.166 and $R^{2}$ of 0.84. We observe that
materials with lower $E_{\mathrm{g}}$ (<4 eV) generally lie close to
the regression line, while the deviation becomes greater for materials
with $E_{\mathrm{g}}>$4 eV, which has also been observed in the
$E_{\mathrm{b}}-E_{\mathrm{g}}$ relation of 2D materials
\cite{Olsen_2016_hydrogen,Jiang_2017_Eg_Eb}. We also observe that
$E_{\mathrm{g}}$ calculated on the HSE06 level shows better linear
correlation with $1/\alpha^{\parallel}$ compared with the bandgap
calculated using the Perdew–Burke–Ernzerhof (PBE) method (details see
Supplementary Information SXX \todo{TBD}). This can be explained by
the fact that the HSE06 hybrid functionals generally have a better
prediction for the bandgap of a material than the PBE method
\todo{some reference?}. It should be noted that although even more
accurate estimation of both $\varepsilon$ and $E_{\mathrm{g}}$ can be
achieved via many-body Green’s function method (GW) together with the
Bethe-Salpeter equation (BSE), the convergence of such method is known
to be highly affected by the dielectric screening of 2D materials
\cite{Hueser_2013_2Dvs3D} (see Supplementary Section SXX
\todo{}). Combining the accuracy, computational effort and
convergence, the choice of the HSE06 hybrid functional may be most
suitable to present the true relationship between $\alpha^{\parallel}$
and $E_{\mathrm{g}}$.

@@

\subsection{Theoretical Explanations}
\label{sec:theory}

@@

>>>>

We study several types of 2D materials of different electronic and
optical properties, including transition metal dichalcogenides (TMDCs,
with the formula MX\(_{\text{2}}\), where M is a metal in group 4, 6,
10 and X=O, S, Se, Te), metal monochalcogenides (Ga$_{2}$S$_{2}$,
Ga$_{2}$Se$_{2}$), cadmium halides (CdX$_2$, X=Cl, I), hexagonal boron
nitride (BN), graphene derivatives (fluorographene (C$_{2}$F$_{2}$),
graphane (C$_{2}$H$_{2}$)) and phosphorene (P$_{4}$).  For the TMDCs,
we consider 2 lattice phases, namely the 2H (P\(\bar{6}\)m2 space
group) and 1T (P3m1 space group).  The structures and elements of the
2D materials are shown in Figure \ref{fig-2}a and \ref{fig-2}b,
respectively. The static 2D polarizabilities are calculated from the
static dielectric response of the selected 2D materials using density
functional theory (DFT) with the Heyd-Scuseria-Ernzerhof hybrid
functionals (HSE06) using the Vienna Ab Initio Simulation Package (VASP)
including spin-orbit coupling to avoid limitations on the description
of band gaps and dielectric functions. Further details for the first
principle calculations please refer to \textit{Methods}.

Figure \ref{fig-3}a shows the calculated bandgap $E_{\mathrm{g}}$
(blue dots) and polarizabilities (bar plots) of all the 2D materials
investigated, covering a wide bandgap range from far infrared to
ultraviolet. From dimension analysis, it is more intuitive to express
the polarizability as $\alpha/(4 \pi \varepsilon_{0})$, which has unit
of \AA. We find that $\alpha^{\parallel}$ has a general descending
trend when $E_{\mathrm{g}}$ increases. On the other hand, no apparent
trend between $\alpha^{\perp}$ and $E_{\mathrm{g}}$ is observed (more
details see Supplementary Section S2.2).  Combining recent theoretical
findings of the universal linear relation between exciton binding
energy $E_{\mathrm{b}}$ and bandgap $E_{\mathrm{b}}$ of 2D materials
\cite{Choi_linear_2015,Olsen_2016_hydrogen,Jiang_2017_Eg_Eb}, and the
fact that the $E_{\mathrm{b}}$ is roughly inversely proportional to
$\alpha^{\parallel}$ \cite{Pulci_2014}, it is reasonable to guess that
a general Moss-like relation between $E_{\mathrm{g}}$ and
$1/\alpha^{\parallel}$ may exist for 2D materials. On the other hand,
the bandgap-independent relation of $\alpha^{\perp}$ resembles
molecular polarizabilities of conjugate molecules \cite{Davies_1952},
fullerenes \cite{Sabirov_2014} and carbon nanotubes
\cite{Benedict_1995}, which are shown to be geometry-dependent. Next
we show that the universal Moss-like relations exist for both
$\alpha^{\parallel}$ and $\alpha^{\perp}$.

Similar to the treatment of quantum wells (QW), the wavefunction of an
isolated 2D material $\psi(\mathbf{r})$ can be separated into the in-
and out-of-plane components \cite{davies_physics_1997}
$\psi^{\parallel}(\mathbf{\rho})$ and $\psi^{\perp}(z)$, such that
$\psi=\psi^{\parallel}\psi^{\perp}$, where $\mathbf{\rho}=(x, y)$ is
the in-plane coordinate. Using the Bloch theorem, the periodic
$\psi^{\parallel}(\mathbf{\rho})$ can be further expressed as
$\psi^{\parallel}(\mathbf{\rho})=e^{ik\rho}u(\rho)$, where $k$ is the
in-plane wave vector and $u(\rho)$ is periodic function in the
xy-planeAccording to the random phase approximation (RPA)
theory\cite{Adler_1962}, $\varepsilon_{\mathrm{SL}}$ is the
$\mathbf{q} \to 0$ and $\omega \to 0$ limits of the non-interacting
dielectric function $\varepsilon(\mathbf{q}, \omega)$, where
$\mathbf{q}$ is the momentum transfer and $\omega$ is the frequency:
\begin{equation}
  \label{eq:RPA-eps2}
  \varepsilon_{\mathrm{SL}}
  = \lim_{\mathbf{q} \to 0} 1 + \frac{2e^{2}}{\varepsilon_{0} |q|^{2} \Omega}
  \sum_{\mathrm{k, c, v}}
  \frac{|<\psi_{\mathrm{v}}(\mathbf{k})|e^{-i\mathbf{q}\mathbf{r}}|\psi_{\mathrm{c}}(\mathbf{k+q})>|^{2}}
  {E_{\mathrm{c}}(\mathbf{k+q}) - E_{\mathrm{v}}(\mathbf{k})}
  \left[f(\psi_{\mathrm{c}}) - f(\psi_{\mathrm{v}})\right]
\end{equation}
where $e$ is the unit charge, c, v are the conduction and valence
bands, $E$ is the eigenenergy of individual bands, and $f$ is the
Fermi-Dirac distribution function. Taking the limit that $L\to\infty$,
when $\varepsilon^{\perp}_{\mathrm{SL}} \approx 1$, we have
$1-1/\varepsilon^{\perp}_{\mathrm{SL}} \approx
(\varepsilon_{\mathrm{SL}}^{\perp} - 1)$. Combine this with
Eqs. \ref{eq:alpha-para-def}, \ref{eq:alpha-perp-def} and
\ref{eq:RPA-eps2}, and taking the difference between the properties of
in-plane and out-of-plane polarizabilities, we derive the expressions
for $\alpha^{\parallel}$ and $\alpha^{\perp}$ under small perturbation
(details see Supplementary Section SXX \todo{mark!}):
  \label{eq:alpha_para_RPA}
  & \alpha^{\parallel} &= \frac{2e^{2}}
  {(2 \pi)^{2}} \int d^{2}\mathbf{k} \sum_{\mathrm{c, v}}
  \frac{|<u_{\mathrm{v}}(\mathbf{k})|\nabla|u_{\mathrm{v}}(\mathbf{k})>|^{2}}
                         {E_{\mathrm{c}}(\mathbf{k}) - E_{\mathrm{v}}(\mathbf{k})} \\
  \label{eq:alpha_perp_RPA}
  & \alpha^{\perp} &= \frac{2e^{2}}{(2 \pi) ^{2}} \int d^{2}\mathbf{k}
  \sum_{\mathrm{c, v}}
  \frac{|<\psi_{\mathrm{v}}(\mathbf{k})|z|\psi_{\mathrm{c}}(\mathbf{k})>|^{2}}
  {E_{\mathrm{c}}(\mathbf{k}) - E_{\mathrm{v}}(\mathbf{k})}
where the integral is performed within the first Brillouin Zone (BZ)
in the reciprocal $\mathbf{k}$-plane. Although they only differ by the
numerator inside the integral, the distinct behaviors of $u(\rho)$
(periodic function) and $\psi(z)$ (confined to the 2D material) give
rise to the different relations of $\alpha^{\parallel}$ and
$\alpha^{\perp}$. Using the $\mathbf{k} \cdot \mathbf{p}$ theory,
Eq. \ref{eq:alpha_para_RPA} is evaluated to be
$\alpha^{\parallel} = N e^{2}/(2\pi E_{\mathrm{g}})$, where $N$ is the
degeneracy associated with the minimal bandgap
\cite{Jiang_2017_Eg_Eb}. On the contrary, $\psi(z)$ is the solution to
the Schr\"{o}dinger equation Hamiltonian
$\mathcal{H} = -\hbar^{2}/2m^{*} \nabla^{2} + V(z)$, where $\hbar$ is
the reduced Planck constant, $m^{*}$ is reduced mass and $V(z)$ is the
confined Coulombic potential along the z-direction created by the
nuclei \cite{davies_physics_1997,ihn_semiconductor_2009}. Using a
simple particle-in-well model, we show that both the numerator and
denominator parts of Eq. \ref{eq:alpha_perp_RPA} are independent of
$E_{g}$ but instead modulated by the size of the potential confinement
(details see Supplementary Section SXX\todo{note}). We further prove,
using both quantum mechanical and fundamental electrostatic models,
that $\alpha^{\perp}$ is actually proportional to the size of
potential confinement (details see Supplementary Section
SXX\todo{note}), which we may relate with the thickness $\delta$ of
the 2D material. Now we may finally propose the 2D analog of the Moss
relation with both in- and out-of-plane polarizations:
\label{eq:2D-Moss-para}
  &\alpha^{\parallel} &\propto E_{g}^{-1} \\
  \label{eq:2D-Moss-perp}
  &\alpha^{\perp} & \propto \delta
which form the main conclusion of this work.

Figure \ref{fig-3}c
shows $(4 \pi \varepsilon_{0})/\alpha^{\parallel}$ (in \AA{}) as a
function of $E_{\mathrm{g}}$ (in eV) for the 2D materials
investigated, with a linear regression slope of ~0.166 and $R^{2}$ of
0.84. We observe that materials with lower $E_{\mathrm{g}}$ (<4 eV)
generally lie close to the regression line, while the deviation
becomes greater for materials with $E_{\mathrm{g}}>$4 eV, which has
also been observed in the $E_{\mathrm{b}}-E_{\mathrm{g}}$ relation of
2D materials \cite{Olsen_2016_hydrogen,Jiang_2017_Eg_Eb}. We also
observe that $E_{\mathrm{g}}$ calculated on the HSE06 level shows
better linear correlation with $1/\alpha^{\parallel}$ compared with
the bandgap calculated using the Perdew–Burke–Ernzerhof (PBE) method
(details see Supplementary Information SXX \todo{TBD}). This can be
explained by the fact that the HSE06 hybrid functionals generally have
a better prediction for the bandgap of a material than the PBE method
\todo{some reference?}. It should be noted that although even more
accurate estimation of both $\varepsilon$ and $E_{\mathrm{g}}$ can be
achieved via many-body Green’s function method (GW) together with the
Bethe-Salpeter equation (BSE), the convergence of such method is known
to be highly affected by the dielectric screening of 2D materials
\cite{Hueser_2013_2Dvs3D} (see Supplementary Section SXX
\todo{}). Combining the accuracy, computational effort and
convergence, the choice of the HSE06 hybrid functional may be most
suitable to present the true relationship between $\alpha^{\parallel}$
and $E_{\mathrm{g}}$.

@@

\iffalse
\subsection{Theoretical Explanations}
\label{sec:theory}

@@

\fi
